Whats reported in the news?

### 2018-03-13 paper/docs/04_Modelresults_50.Rmd
add correlation

```{r eval=FALSE, fig.height=8, fig.width=4}
topic <- 1

plotQuote(c(paste(sagelabs$covnames[1],":", 
                  paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[2],":",
                  paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[3],":", 
                  paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[4],":", 
                  paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[5],":", 
                  paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[6],":",
                  paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[7],":",
                  paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n"))),
          text.cex = 0.8, width = 40,
          main = paste(topics.df$topic_name[topics.df$topic==topic])
          )
```

@@

```{r}
load("../output/polls.Rda")

htmlTable::htmlTable(table[1:10,], align = "l")
```

Prepare Dataframes

```{r}
polls <- table_long %>%
  mutate(month=month(Datum),
         year = year(Datum),
         yearmonth = calculate_month(month,year)) %>%
  group_by(yearmonth,party) %>%
  summarise(mean_val = mean(value, na.rm=T)) %>%
  ungroup() %>%
  filter(mean_val != "NaN") %>%
  select(party, yearmonth, mean_val) %>%
  spread(party, mean_val)
```

#### CDU

```{r fig.height=12, fig.width=10}
polls.red <- polls %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  mutate(Union = normalize_data(Union))

topics.red <- sentDF.values %>%
  filter(grepl(paste("CDU","CSU","coalition", sep="|"), 
               topic_name, ignore.case = T))

### plot by time
p <-topics.red %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month, by="yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 1  
p1 <- ggplot() +
  geom_col(data=p, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +

  # Add poll line
  geom_line(data = polls.red, 
            aes(yearmonth, Union),
            color = "black",
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

### plot by time and site
p <- topics.red %>%
  group_by(yearmonth, topic_name, topic, site) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 2
p2 <- ggplot() +
  geom_col(data = p,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
  scale_fill_manual(values = col) +
  facet_wrap(~site, ncol = 2) +
   # Add poll line
  geom_line(data = polls.red, 
            aes(yearmonth, Union),
            color = "black",
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

@@

#### SPD
```{r fig.height=12, fig.width=10}
polls.red <- polls %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  mutate(SPD = normalize_data(SPD))

topics.red <- sentDF.values %>%
  filter(grepl(paste("SPD", sep="|"), topic_name, ignore.case = T))

### plot by time
p <-topics.red %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month, by="yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 1  
p1 <- ggplot() +
  geom_col(data=p, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +

  # Add poll line
  geom_line(data = polls.red, 
            aes(yearmonth, SPD),
            color = "red",
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

### plot by time and site
p <- topics.red %>%
  group_by(yearmonth, topic_name, topic, site) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 2
p2 <- ggplot() +
  geom_col(data = p,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
  scale_fill_manual(values = col) +
  facet_wrap(~site, ncol = 2) +
   # Add poll line
  geom_line(data = polls.red, 
            aes(yearmonth, SPD),
            color = "red",
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

@@

#### FDP

```{r fig.height=12, fig.width=10}
polls.red <- polls %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  mutate(FDP = normalize_data(FDP))

topics.red <- sentDF.values %>%
  filter(grepl(paste("Jamaica", sep="|"), 
               topic_name, ignore.case = T))

### plot by time
p <-topics.red %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month, by="yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 1  
p1 <- ggplot() +
  geom_col(data=p, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +

  # Add poll line (FDP)
  geom_line(data = polls.red, 
            aes(yearmonth, FDP),
            color = col[4],
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

### plot by time and site
p <- topics.red %>%
  group_by(yearmonth, topic_name, topic, site) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 2
p2 <- ggplot() +
  geom_col(data = p,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
  scale_fill_manual(values = col) +
  facet_wrap(~site, ncol = 2) +
    # Add poll line (FDP)
  geom_line(data = polls.red, 
            aes(yearmonth, FDP),
            color = col[4],
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

#### B90 / Die Grüne

```{r fig.height=12, fig.width=10}
polls.red <- polls %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  mutate(Grüne = normalize_data(Grüne))

topics.red <- sentDF.values %>%
  filter(grepl(paste("Jamaica","Grüne", sep="|"), 
               topic_name, ignore.case = T))

### plot by time
p <-topics.red %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month, by="yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 1  
p1 <- ggplot() +
  geom_col(data=p, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +

    # Add poll line (Grüne)
  geom_line(data = polls.red, 
            aes(yearmonth, Grüne),
            color = "limegreen",
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

### plot by time and site
p <- topics.red %>%
  group_by(yearmonth, topic_name, topic, site) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 2
p2 <- ggplot() +
  geom_col(data = p,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
  scale_fill_manual(values = col) +
  facet_wrap(~site, ncol = 2) +

    # Add poll line (Grüne)
  geom_line(data = polls.red, 
            aes(yearmonth, Grüne),
            color = "limegreen",
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

#### AfD

```{r fig.height=12, fig.width=10}
polls.red <- polls %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  mutate(AfD = normalize_data(AfD))

topics.red <- sentDF.values %>%
  filter(grepl(paste("AfD", sep="|"), 
               topic_name, ignore.case = T))

### plot by time
p <-topics.red %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month, by="yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 1  
p1 <- ggplot() +
  geom_col(data=p, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +

    # Add poll line (AfD)
  geom_line(data = polls.red, 
            aes(yearmonth, AfD),
            color = "skyblue",
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

### plot by time and site
p <- topics.red %>%
  group_by(yearmonth, topic_name, topic, site) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### Plot 2
p2 <- ggplot() +
  geom_col(data = p,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
  scale_fill_manual(values = col) +
  facet_wrap(~site, ncol = 2) +

    # Add poll line (AfD)
  geom_line(data = polls.red, 
            aes(yearmonth, AfD),
            color = "skyblue",
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

>>>>

```{r eval=FALSE, fig.height=8, fig.width=4}
topic <- 2

plotQuote(c(paste(sagelabs$covnames[1],":", 
                  paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[2],":",
                  paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[3],":", 
                  paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[4],":", 
                  paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[5],":", 
                  paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[6],":",
                  paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[7],":",
                  paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n"))),
          text.cex = 0.8, width = 40
          )
```

@@

We use the data from the "Sonntagsumfrage" (Sunday survey) from [infratest dimap](https://www.infratest-dimap.de/umfragen-analysen/bundesweit/sonntagsfrage/). The institution regularly asks at least 1000 German citizens the question: "Which party would you choose if federal elections take place next Sunday?" The survey thus measures the current election tendencies and therefore reflects an intermediate state in the opinion-forming process of the electoral population.

The comparison with the sentiment value of individual topics is intended to show whether there is a correlation between the current tendency to vote and the type of reporting. For this purpose, the monthly average of both time series is calculated and rescaled to an interval between 0 and 1.

The analysis in this section is done in two steps: First, the standardised time series are compared graphically. In the second step, the cross-correlation between two time series is calculated.

###### Normalization

$$
z_i = \frac{x_i-\text{min}(x)}{\text{max}(x)-\text{min}(x)}
$$
where $x = (x_1,...,x_n)$ and $z_i$ is the $i^{th}$ normalized data.

```{r}
# Import and prepare survey data
load("../output/polls.Rda")

polls <- table_long %>%
  mutate(month=month(Datum),
         year = year(Datum),
         yearmonth = calculate_month(month,year)) %>%
  group_by(yearmonth,party) %>%
  summarise(mean_val = mean(value, na.rm=T)) %>%
  ungroup() %>%
  filter(mean_val != "NaN") %>%
  select(party, yearmonth, mean_val) %>%
  spread(party, mean_val)
```

```{r fig.height=12, fig.width=10}
polls.red <- polls %>%
  filter(yearmonth > as.Date("2017-05-01")) %>%
  transmute(Union = normalize_data(Union),
         SPD = normalize_data(SPD),
         Grüne = normalize_data(Grüne),
         FDP = normalize_data(FDP),
         AfD = normalize_data(AfD),
         yearmonth = yearmonth)

# topics.red <- sentDF.values %>%
#   filter(grepl(paste("CDU","CSU","coalition", sep="|"), 
#                topic_name, ignore.case = T))
### by time
group1 <- sentDF.values %>%
  group_by(yearmonth, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month, by="yearmonth") %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))

### by time and site
group2 <- sentDF.values %>%
  group_by(yearmonth, topic_name, topic, site) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            obs = n()) %>%
  ungroup() %>%
  left_join(., tally_month_site, by=c("yearmonth","site")) %>%
  mutate(w = obs / total_obs,
         sentiment_w = sentiment * w,
         sentiment_n = normalize_data(sentiment_w))
```

```{r fig.height=5, fig.width=10}
ggplot(group1, aes(yearmonth, 
                   sentiment_n, 
                   group = topic_name,
                   color = topic_name)) +
  geom_line(show.legend = F) +
  facet_wrap(~topic_name, nrow = 3) +
  labs(x="", y="", title="Sentiment Score")
```

```{r}
polls.red %>%
  gather(key = party, value = poll, Union:AfD) %>%
  ggplot(aes(yearmonth, poll, color = party)) +
  geom_line() +
  labs(x="", y="", title = "Survey Value", color = "")
```

#### 3.1. Cross-Correlation
```{r}
group1 %>%
  select(yearmonth, topic_name, sentiment_n) %>%
  spread(topic_name, sentiment_n) %>%
  select(- yearmonth) -> corr1

polls.red %>% select(- yearmonth) -> corr2

corr <- expand.grid(names(corr1), names(corr2))
corr$correlation <- NA
```

```{r}
x <- 1

for (corr1Id in 1:ncol(corr2)) {
  c1 = corr2[,corr1Id]
  #print(names(corr2[,corr1Id]))
  for(corr2Id in 1:ncol(corr1)) {
    c2 = corr1[,corr2Id]
    #print(names(corr1[,corr2Id]))
    correlation = ccf(c1, c2, lag.max = 0,
                      na.action = na.contiguous, plot=F)
    corr[x,3] <- correlation$acf[1]

    x<- x+1
  }
}
```

```{r}
ggplot(corr, aes(Var2, Var1,
                 fill = correlation,
                 label = round(correlation,2))) +
  geom_tile(color="white") +
  geom_text(size = 3, color = col[5]) +
  viridis::scale_fill_viridis() +
  labs(x="", y="", title = "Cross Correlation of Polls vs. Sentiment Value")
```

#### 3.2. Graphical analysis

##### 3.2.1. CDU
```{r fig.height=10, fig.width=12}
### Plot 1  
plot1 <- group1 %>%
  filter(grepl(paste("CDU","CSU",sep="|"), topic_name))

p1 <- ggplot() +
  geom_col(data=plot1, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
    geom_line(data=plot1, aes(yearmonth, sentiment_n, 
             group = topic_name,
             color = topic_name),
             show.legend = F) +
  scale_color_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +
  # Add poll line
  geom_line(data = polls.red, 
            aes(yearmonth, Union),
            color = "black",
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

### Plot 2
plot2 <- group2 %>%
  filter(grepl(paste("CDU","CSU",sep="|"), topic_name))

p2 <- ggplot() +
  geom_col(data = plot2,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
    scale_fill_manual(values = col) +
    scale_color_manual(values = col) +
  geom_line(data = plot2,
            aes(yearmonth, sentiment_n,
                group = topic_name,
                color = topic_name),
            show.legend = F) +
  facet_wrap(~site, ncol = 2) +
   # Add poll line
  geom_line(data = polls.red, 
            aes(yearmonth, Union),
            color = "black",
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

@@

#### SPD
```{r fig.height=12, fig.width=10}
plot1 <- group1 %>%
  filter(grepl(paste("SPD", sep="|"), topic_name, ignore.case = T))

### Plot 1  
p1 <- ggplot() +
  geom_col(data=plot1, aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           position = "dodge", 
           alpha = 0.8) +
  scale_fill_manual(values = col) +
  guides(fill = guide_legend(ncol=3)) +
   geom_line(data=plot1, aes(yearmonth, sentiment_n, 
             group = topic_name,
             color = topic_name),
             show.legend = F) +
  scale_color_manual(values = col) +
  # Add poll line
  geom_line(data = polls.red, 
            aes(yearmonth, SPD),
            color = "red",
            size = 1) +
  labs(y="", x="", fill="",
       title = "Sentiment & Poll Values",
       subtitle = "Both scores are normalized") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "bottom")

### plot by time and site
plot2 <- group2 %>%
  filter(grepl(paste("SPD", sep="|"), topic_name, ignore.case = T))

### Plot 2
p2 <- ggplot() +
  geom_col(data = plot2,
           aes(yearmonth, sentiment_n, 
             group = topic_name,
             fill = topic_name),
           alpha = 0.8,
           position = "dodge") +
  scale_fill_manual(values = col) +
  facet_wrap(~site, ncol = 2) +
     geom_line(data=plot2, aes(yearmonth, sentiment_n, 
             group = topic_name,
             color = topic_name),
             show.legend = F) +
  scale_color_manual(values = col) +
   # Add poll line
  geom_line(data = polls.red, 
            aes(yearmonth, SPD),
            color = "red",
            size = 1) +
  labs(y="", x="", fill="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 90))

@@
